They Work for You may be subject to challenges of finance and the types of users accessing the site, as described with Appndix E and F, respectively.
In addition, their apparent use of Google Analytics is outlined in Appendix D. 
Nevertheless, it is suggested that the primary challenge facing the site is one that directly results from its provision of open, automated data.
That is, the site focuses attention on MPs voting patterns and not on the broader aspects of their roles within communities or, indeed, parliament.

One example of the dochotomy between an MPs voting patterns and their community work concerns former University of Edinburgh student Ian Murray \cite{ian-murray}, who has been the MP for the Edinburgh South constituency since the UK 2010 general election. 
In 2015, Hearts of Midlothian football club, which was founded in 1874, and which is one of the two football professional clubs in Edinburgh, faced closure following the bankruptcy of its Russian owner, Vladimir Romanov.
As a consequence of his role as the local MP, Ian Murray was asked by supporters of the club to liase with the club's official receivers.
Over several years, his work led to a supports buyout the club, which is now the only football club in the Scottish Premier League owned by its supporters.
Ian Murray was subsequently interviewed \cite{ian-murray-bbc} on the BBC Parliametrary channel \cite{bbc-parliament} with regard to a book he wrote, This is our story \cite{ian-murray-this-is-our-story}, describing his voluntary work.
However, while Ian Murray’s involvement came about because of his role as an MP, it did not involve any specific questions in the commons.
Consequently, is not described by the aggregated data on his They Work for You page, as can be seen from the screen shot within Figure \ref{fig:they-work-for-you-ian-murray}.

